Predicting FOMC Actions Using ML and NLP

### 2019-05-05 presentation/presentation.tex
update
JLs presentation proposal
update presentation slide

\usepackage{comment}
%usepackage{appendixnumberbeamer}
%\usepackage{amsmath}
\usepackage{pgfpages}
% citations
\usepackage{natbib}
\bibpunct{(}{)}{;}{a}{,}{,}
\def\citeapos#1{\citeauthor{#1}'s (\citeyear{#1})}
\renewcommand{\bibsection}{\subsubsection*{\bibname } }

\title{Modelling Federal Open Market Committee Decisions Using ML and NLP}

@@

% - Use the \inst{?} command only if the authors have different
%   affiliation.
%\author{F.~Author\inst{1} \and S.~Another\inst{2}}
\author{Jeremy Lao \& John Reynolds}

@@

\date{Date}

@@

\begin{frame}
\titlepage
\end{frame}

\begin{frame}

\begin{figure}[h!]
\includegraphics[width=1\textwidth]{../output/data_for_graphs/Topic-Model-3-topics.PNG}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_lasso_f1".pdf}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/naive_bayes_f1".pdf}
\end{center}
\end{figure}

>>>>

\usepackage{comment}
%usepackage{appendixnumberbeamer}
%\usepackage{amsmath}
\usepackage{pgfpages}
\usepackage{float}
% citations
\usepackage{natbib}
\usepackage{lipsum}
\usepackage[export]{adjustbox}
\usepackage{subfig}

\bibpunct{(}{)}{;}{a}{,}{,}
\def\citeapos#1{\citeauthor{#1}'s (\citeyear{#1})}
\renewcommand{\bibsection}{\subsubsection*{\bibname } }

\title{Predicting FOMC Actions Using ML and NLP}

@@

% - Use the \inst{?} command only if the authors have different
%   affiliation.
%\author{F.~Author\inst{1} \and S.~Another\inst{2}}
\author{Jeremy Lao - jjl359  \& John Reynolds - jr4716}

@@

\date{May-7-2019}

@@

\begin{frame}
\frametitle {Predicting FOMC Actions Using ML and NLP  \\Jeremy Lao - jjl359  \& John Reynolds - jr4716 }

\small \textbf{Model-1: FOMC Decison $D_t$ based on lagged document text}
\vspace{-2mm}
\begin{small}
$$E[D_t | \mbox{Statements}_{t-i}, \mbox{Minutes}_{t-j} , \mbox{Speeches}_{t-k}, \mbox{N-gram}]$$
\end{small}
\vspace{-2.5mm}
\small \textbf{Model-2: FOMC Decison $D_t$ based on aggregated lagged document text}
\begin{small}
$$E[D_t | \mbox{AGG}(\mbox{Statements}_{t-i}, \mbox{Minutes}_{t-j} , \mbox{Speeches}_{t-k}), \mbox{N-gram}]$$
\end{small}

\vspace{-7mm}

\noindent \center {\small where} {$D_t = 1$}{\small, if change to rates,} {$D_t = 0$}{\small, if no change.}

\vspace{-5mm}
\begin{figure}[h]
  \subfloat
   {\includegraphics[width=.5\textwidth]{./model1.jpg}  
   \hspace{10px}} 
  \includegraphics[width=.5\textwidth]{./model2.jpg}
  \captionsetup{labelformat=empty}
  \caption{x-axis: Ngram, y-axis: F1 Score}
\end{figure}
